Methods

### 2023-12-01 methods.qmd
Incorporated code to rectify 2021 lsoa to 2011 lsoa into the targets pathway

@@

Have decided to use October 2022 and also downloaded the GP to icb mapping file from the same period

>>>>

Have opted for the latter solution.

@@

Have decided to use October 2022 and also downloaded the GP to icb mapping file from the same period and joined to the gp list size to easily create analysis by icb/sub-icb.

## Clustering

### Attempt 1
